Toward \earlywarning\ detection of gravitational waves from compact binary coalescence

### 2011-10-12 article.tex
Corrected comments related to Fisher matrix
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1395 ccdd05d5-56c1-461a-bf98-85f6876523b4

\EM\ followup requires estimating the location of the \GW\ source. The localization
uncertainty can be estimated from the uncertainty in the time of arrival of the \GW{}s,
which is determined by the signal's effective bandwidth and \SNR\
\citep{Fairhurst2009}.  Table~\ref{fig:earlywarning} and
Figure~\ref{fig:sky-localization-accuracy} show the estimated 90\%
confidence area versus time of the loudest coalescence events detectable by
Advanced \LIGO\ and Advanced Virgo.  This is the \emph{minimum} area; localization
is best at high elevation from the plane containing the detectors and worst at zero elevation.
As \citeauthor{Fairhurst2009} cautions, his formula also slightly \emph{overestimates} the minimum localization uncertainty for low SNR events because it makes an approximation that the timing errors are Gaussian distributed.  Nonetheless, given the large uncertainties in rates, these approximations suffice for an order of magnitude estimate.
Once per year, we expect to observe an
event with a final single-detector \SNR\ of $\approx$27 whose location can be constrained to about
1300~deg$^2$ (3.1\% of the sky) within 25~s of merger,
260~deg$^2$ (0.63\% of the sky) within 10~s of merger, and
0.82~deg$^2$ (0.0020\% of the sky) at merger.

>>>>

\EM\ followup requires estimating the location of the \GW\ source. The localization
uncertainty can be estimated from the uncertainty in the time of arrival of the \GW{}s,
which is determined by the signal's effective bandwidth and \SNR\
\citep{Fairhurst2009}.  Table~\ref{fig:earlywarning} and
Figure~\ref{fig:sky-localization-accuracy} show the estimated 90\%
confidence area versus time of the loudest coalescence events detectable by
Advanced \LIGO\ and Advanced Virgo.  This is the \emph{minimum} area; localization is best at high elevation
from the plane containing the detectors and worst at zero elevation. As
\citeauthor{Fairhurst2009} cautions, his formula also slightly
\emph{overestimates} the minimum area for low SNR events because it
makes an approximation that the timing errors are Gaussian distributed
and that the sky location estimates are Gaussian distributed about the
true location.  Nonetheless, given the large uncertainties in rates,
\citeauthor{Fairhurst2009}'s approximations suffice for an order of
magnitude estimate.
Once per year, we expect to observe an
event with a final single-detector \SNR\ of $\approx$27 whose location can be constrained to about
1300~deg$^2$ (3.1\% of the sky) within 25~s of merger,
260~deg$^2$ (0.63\% of the sky) within 10~s of merger, and
0.82~deg$^2$ (0.0020\% of the sky) at merger.
